Point-process based representation learning for Electronic Health Records

### 2023-01-30 Manuscript_v1.tex
commit

@@

\subsection{Time concatenation}

@@

@@

one advantage of proposed method is use of attention mechanisms in both event and state encoder.
Fig 1 shows the attention mechanism
% Please add the following required packages to your document preamble:
% \usepackage{multirow}
% \usepackage{graphicx}
\begin{table}[h!]
    \centering
    \caption{unsupervised learning}
    \label{tab:table1}
    \resizebox{\columnwidth}{!}{%    
    \begin{tabular}{cclllll}
    \hline
    \multirow{2}{*}{Dataset} & \multicolumn{2}{c}{Model}            & \multicolumn{2}{c}{next mark} & next time & CIFs  \\
                             & \multicolumn{1}{l}{module} & loss    & AUPRC         & AUROC         & RMSE      & NLL   \\ \hline
    \multirow{6}{*}{p12}     & \multirow{3}{*}{TE}        & MC      & 23.98         & 23.98         & 23.98     & 23.98 \\
                             &                            & ML      & 23.98         & 23.98         & 23.98     & 23.98 \\
                             &                            & SHPMARK & 23.98         & 23.98         & 23.98     & 23.98 \\
                             & \multirow{3}{*}{TEDA}      & MC      & 23.98         & 23.98         & 23.98     & 23.98 \\
                             &                            & ML      & 23.98         & 23.98         & 23.98     & 23.98 \\
                             &                            & SHPMARK & 23.98         & 23.98         & 23.98     & 23.98 \\ \hline
    \multirow{6}{*}{p19}     & \multirow{3}{*}{TE}        & MC      & 23.98         & 23.98         & 23.98     & 23.98 \\
                             &                            & ML      & 23.98         & 23.98         & 23.98     & 23.98 \\
                             &                            & SHPMARK & 23.98         & 23.98         & 23.98     & 23.98 \\
                             & \multirow{3}{*}{TEDA}      & MC      & 23.98         & 23.98         & 23.98     & 23.98 \\
                             &                            & ML      & 23.98         & 23.98         & 23.98     & 23.98 \\
                             &                            & SHPMARK & 23.98         & 23.98         & 23.98     & 23.98 \\ \hline
    \end{tabular}%
    }
\end{table}

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
% \usepackage{graphicx}
\begin{table}[h!]

    \centering
    \caption{Transfer learnings}
    \label{tab:table2}
    \resizebox{\columnwidth}{!}{%
    \begin{tabular}{|cll|ll|ll|}
    \hline
    \multicolumn{3}{|c|}{model}                                                          & \multicolumn{2}{c|}{p12}           & \multicolumn{2}{c|}{p19}           \\ \hline
    \multicolumn{1}{|l|}{module}                & \multicolumn{1}{l|}{loss}    & freezed & \multicolumn{1}{l|}{AUPRC} & AUROC & \multicolumn{1}{l|}{AUPRC} & AUROC \\ \hline
    \multicolumn{1}{|c|}{\multirow{3}{*}{TE}}   & \multicolumn{1}{l|}{MC}      &         & \multicolumn{1}{l|}{23.98} & 23.98 & \multicolumn{1}{l|}{23.98} & 23.98 \\ \cline{2-7} 
    \multicolumn{1}{|c|}{}                      & \multicolumn{1}{l|}{ML}      &         & \multicolumn{1}{l|}{23.98} & 23.98 & \multicolumn{1}{l|}{23.98} & 23.98 \\ \cline{2-7} 
    \multicolumn{1}{|c|}{}                      & \multicolumn{1}{l|}{SHPMARK} &         & \multicolumn{1}{l|}{23.98} & 23.98 & \multicolumn{1}{l|}{23.98} & 23.98 \\ \hline
    \multicolumn{1}{|c|}{\multirow{3}{*}{TEDA}} & \multicolumn{1}{l|}{MC}      &         & \multicolumn{1}{l|}{23.98} & 23.98 & \multicolumn{1}{l|}{23.98} & 23.98 \\ \cline{2-7} 
    \multicolumn{1}{|c|}{}                      & \multicolumn{1}{l|}{ML}      &         & \multicolumn{1}{l|}{23.98} & 23.98 & \multicolumn{1}{l|}{23.98} & 23.98 \\ \cline{2-7} 
    \multicolumn{1}{|c|}{}                      & \multicolumn{1}{l|}{SHPMARK} &         & \multicolumn{1}{l|}{23.98} & 23.98 & \multicolumn{1}{l|}{23.98} & 23.98 \\ \hline
    \end{tabular}%
    }
    \end{table}

>>>>

\subsection{Effect of minor improvements}

effect of time concatenation

compare single+mark with mc or ml

\begin{table}[h!]
\centering
\caption{Effect}
\label{tab:my-table}
\begin{tabular}{lllll}
        &        & shp+mark &     & baseline \\ \cline{3-5} 
Dataset & Metric & concat   & sum &          \\ \hline
SO      & NLL    &          &     &          \\
        & AUROC  &          &     &          \\
        & time   &          &     &          \\ \hline
Synthea & NLL    &          &     &          \\
        & AUROC  &          &     &          \\
        & time   &          &     &          \\ \hline
ReTweet & NLL    &          &     &          \\
        & AUROC  &          &     &          \\
        & time   &          &     &          \\ \hline
\end{tabular}
\end{table}

@@

\begin{table}[h!]
\centering
\caption{NLL estimation}
\label{tab:my-table}
\begin{tabular}{lllll}
\hline
        &         &    & Model  &          \\ \cline{3-5} 
Dataset & setting & TE & TE+DAM & TE+noise \\ \hline
P12     & sc      &    &        &          \\
        & mc1     &    &        &          \\
        & mc2     &    &        &          \\ \hline
p19     & sc      &    &        &          \\
        & mc1     &    &        &          \\
        & mc2     &    &        &          \\ \hline
\end{tabular}
\end{table}

can u provide one example patient?

@@

% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table*}
\centering
\caption{Down stream task}
\label{tab:my-table}
\begin{tabular}{cccccccccccc}
\hline
                     &                      &        &  & F1   &        &  & AUPRC &        &  & AUROC &        \\ \cline{5-6} \cline{8-9} \cline{11-12} 
Dataset              & Setting              & Center &  & DAM  & TE+DAM &  & DAM   & TE+DAM &  & DAM   & TE+DAM \\ \hline
\multirow{8}{*}{P12} & \multirow{3}{*}{sc}  & 1      &  & 0.55 & 0.55   &  & 0.55  & 0.55   &  & 0.55  & 0.55   \\
                     &                      & 2      &  & 0.55 & 0.55   &  & 0.55  & 0.55   &  & 0.55  & 0.55   \\
                     &                      & 3      &  & 0.55 & 0.55   &  & 0.55  & 0.55   &  & 0.55  & 0.55   \\ \cline{2-12} 
                     & \multirow{3}{*}{mc1} & 1      &  & 0.55 & 0.55   &  & 0.55  & 0.55   &  & 0.55  & 0.55   \\
                     &                      & 2      &  & 0.55 & 0.55   &  & 0.55  & 0.55   &  & 0.55  & 0.55   \\
                     &                      & 3      &  & 0.55 & 0.55   &  & 0.55  & 0.55   &  & 0.55  & 0.55   \\ \cline{2-12} 
                     & mc2                  & -      &  & 0.55 & 0.55   &  & 0.55  & 0.55   &  & 0.55  & 0.55   \\
                     & seft                 & -      &  & 0.55 & 0.55   &  & 0.55  & 0.55   &  & 0.55  & 0.55   \\ \hline
\multirow{8}{*}{P19} & \multirow{3}{*}{sc}  & 1      &  & 0.55 & 0.55   &  & 0.55  & 0.55   &  & 0.55  & 0.55   \\
                     &                      & 2      &  & 0.55 & 0.55   &  & 0.55  & 0.55   &  & 0.55  & 0.55   \\
                     &                      & 3      &  & 0.55 & 0.55   &  & 0.55  & 0.55   &  & 0.55  & 0.55   \\ \cline{2-12} 
                     & \multirow{3}{*}{mc1} & 1      &  & 0.55 & 0.55   &  & 0.55  & 0.55   &  & 0.55  & 0.55   \\
                     &                      & 2      &  & 0.55 & 0.55   &  & 0.55  & 0.55   &  & 0.55  & 0.55   \\
                     &                      & 3      &  & 0.55 & 0.55   &  & 0.55  & 0.55   &  & 0.55  & 0.55   \\ \cline{2-12} 
                     & mc2                  & -      &  & 0.55 & 0.55   &  & 0.55  & 0.55   &  & 0.55  & 0.55   \\
                     & seft                 & -      &  & 0.55 & 0.55   &  & 0.55  & 0.55   &  & 0.55  & 0.55   \\ \hline
\end{tabular}
\end{table*}

@@

one advantage of proposed method is use of attention mechanisms in both event and state encoder.
Fig 1 shows the attention mechanism
